paper1_results_figs_slimmed_50

### 2016-03-16 paper1_results_figs_slimmed_50.Rmd
add some mix2 plots and calc of the lm line

  dif_mixA_seq <- cbind(resistPointsMix_A_T[-indices1], tmp)

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.5 > 500 | dif_mixA_seq$gen_cP0.5seq > 500 )

  #subset by runs not making threshold
  dif_mixA_seq <- dif_mixA_seq[-didntReachThresh,]

  #dif_mixA_seq$mixA_minus_seq0.5 <- dif_mixA_seq["gen_cP0.5"] - dif_mixA_seq["gen_cP0.5seq"]
  dif_mixA_seq["mixA_minus_seq0.5"] <- dif_mixA_seq["gen_cP0.5"] - dif_mixA_seq["gen_cP0.5seq"]

  #TODO : later do PRCC on dif_mixA_seq["mixA_minus_seq0.5"]

@@

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      #scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Sole use", "Mix either"="1st in mix","Sequential"="2nd in sequence", "Mix adaptive"="2nd in mix\nswitch to sole", "Mix both"="2nd in mix" ) )
      scale_x_discrete("Resistance to which insecticide", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Sole use", "Mix either"="1st in mix","Sequential"="2nd in sequence", "Mix adaptive"="adaptive mix", "Mix both"="2nd in mix" ) )

@@

    #draw_plot(p,x=0,y=0,width=.5,height = .5)

    # print( ggdraw() + #panel_border(remove = TRUE) +
    #          draw_plot( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) +     
    # #print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
    #          geom_point(shape=1, colour='red') +
    #          theme(axis.text.x = axis_text_x) +
    #          #theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
    #          geom_hline(yintercept = 0, linetype=3) +
    #          ylim(-1,1) +
    #          #ggtitle(paste(strategy,"PRCC")) +
    #          ggtitle(paste(strategy,"time-to-resistance 0.5")) +
    #          xlab(NULL)
    #       , height= height))

@@

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
              "dominance_allele1","selection_coef_allele1","maleExposureProp")
  out_cols <- c("time_to_resistance0.5","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

@@

    x <- dif_mixA_seq[,1:num_inputs]
    y <- dif_mixA_seq["mixA_minus_seq0.5"]

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             ylim(-1,1) +
             #ggtitle(paste("PRCC difference between sequential and mixture adaptive")) +
             xlab(NULL)
          )

@@

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )       
```

@@

    #adds in no. scenarios correctly and incorrectly classified
    #prp(tree, extra=1, varlen = 10, main=treeResponse)
    #prp(treePruned, extra=1, varlen = 10, main=treeResponse, col=cols, border.col=cols)
    #prp(treePruned, extra=1, varlen = 0, main=treeResponse, box.col=cols, under=TRUE)
    prp(treePruned, extra=1, varlen = 0, main='', box.col=cols, under=TRUE)
    }

>>>>

  dif_mixA_seq <- cbind(resistPointsMix_A_T[-indices1], tmp)
  dif_mix2_seq <- cbind(resistPointsMix_2_T[-indices1], tmp)

  #remove runs that didn't reach a resistance threshold (999), even if just for one strategy
  #>1000 excludes sequential strategy that had a 999 in
  #BEWARE would need to increase 1000 if I increase max generations in the runs
  didntReachThresh <- which( dif_mixA_seq$gen_cP0.5 > 500 | dif_mixA_seq$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_mixA_seq <- dif_mixA_seq[-didntReachThresh,]

  dif_mixA_seq["mixA_minus_seq0.5"] <- dif_mixA_seq["gen_cP0.5"] - dif_mixA_seq["gen_cP0.5seq"]

  #for dif_mix2_seq
  didntReachThresh <- which( dif_mix2_seq$gen_cP0.5 > 500 | dif_mix2_seq$gen_cP0.5seq > 500 )
  #subset by runs not making threshold
  dif_mix2_seq <- dif_mix2_seq[-didntReachThresh,]

  dif_mix2_seq["mix2_minus_seq0.5"] <- dif_mix2_seq["gen_cP0.5"] - dif_mix2_seq["gen_cP0.5seq"]

@@

  print( ggplot(ggSubset, aes_string(x='strategy',y=i, color='strategy')) + 
      #ylim(0,450) +
      coord_cartesian( ylim=c(0, 350)) +
      geom_violin(draw_quantiles = c(0.25, 0.75), show.legend=FALSE, adjust = .5 ) +
      ylab('time to resistance (gens)') +
      scale_x_discrete("", limits=c("insecticide 1","Mix either","Sequential","Mix adaptive","Mix both"), labels = c("insecticide 1"="Seq (1st)", "Mix either"="Mix (1st)","Sequential"="Seq (2nd)", "Mix adaptive"="adaptive", "Mix both"="Mix (2nd)" ) )

@@

@@

  #remove insecticide1 & 2 strategies
  ggSubset <- ggInsOuts[ !ggInsOuts$strategy %in% c("insecticide 1","insecticide 2"), ]
  #subset which output plots to show in the main paper
  # in_cols <- c("start_freq_allele1", "exposure","effectiveness_insecticide1",
  #             "dominance_allele1","selection_coef_allele1","maleExposureProp")
  in_cols <- c("exposure","effectiveness_insecticide1","dominance_allele1")

  out_cols <- c("time_to_resistance0.5","strategy")
  ggSubset <- ggSubset[, c(in_cols,out_cols) ]

@@

    #mixture2
    x <- dif_mix2_seq[,1:num_inputs]
    y <- dif_mix2_seq["mix2_minus_seq0.5"]

@@

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             ylim(-1,1) +
             xlab(NULL)
          )

    ## repeat code for adaptive
    x <- dif_mixA_seq[,1:num_inputs]
    y <- dif_mixA_seq["mixA_minus_seq0.5"]

    print( ggplot( to_plot, aes_string(x='inputs',y='PRCC') ) + 
             geom_point(shape=1, colour='red') +
             theme(axis.text.x = element_text(angle = 45,hjust = 1, vjust = 1)) +
             geom_hline(yintercept = 0, linetype=3) +
             #theme_bw() +
             ylim(-1,1) +
             xlab(NULL)
          )

@@

             #add text for Curtis point
             geom_label(data = curtisInputs, inherit.aes = FALSE, aes_string(x = 'exposure', y='effectiveness_insecticide1 + effectiveness_insecticide2', label='"Curtis Fig.2"', hjust='"right"'), nudge_x=-0.02, size=3, colour='red')
           )

  # doing the lm outside of ggplot    
  #df_same = ggSubset[which(ggSubset$mixA_minus_seq0.5==0),]
  x1=df_same$exposure 
  y1=df_same$effectiveness_insecticide1 + df_same$effectiveness_insecticide2

  l_mod <- lm(y1 ~ x1)
  l_mod$coefficients
  #(Intercept)           x 
  #  0.9790948   0.6095132 
  #l_mod$coefficients
  #(Intercept)          x1 
  #1.019330    0.560508

  #approximation
  #x2 <- seq(0,1,0.1)
  #y2 <- 0.6*x2+0.98
  #plot(x2,y2)

@@

    #add fig label
    if (treeResponse == treeResponses[1]) main <- "A)" 
    else  main <- "B)"

    #adds in no. scenarios correctly and incorrectly classified
    #prp(tree, extra=1, varlen = 10, main=treeResponse)
    #prp(treePruned, extra=1, varlen = 10, main=treeResponse, col=cols, border.col=cols)
    #prp(treePruned, extra=1, varlen = 0, main=treeResponse, box.col=cols, under=TRUE)
    prp(treePruned, extra=1, varlen = 0, main=main, box.col=cols, under=TRUE)
    }
